Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb

### 2018-03-18 nb_px_paper/nb_px_paper.tex
Updated variance minimization, Na22/24 subtraction, and final fluence plot.

Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions needed to establish beam characteristics in this energy range needed to perform quantitative cross section measurements.  
To address this need, a target stack consisting of thin Nb, Cu, and Al monitor foils using a 100 MeV proton beam at the Los Alamos National Laboratory's Isotope Production Facility was irradiated in order to establish \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} as a reaction monitor for intermediate energy protons and to benchmark state-of-the-art reaction model codes in this energy region.
% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
Cross sections were measured using the well-characterized 
% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence determination, with all activities quantified using high-purity germanium spectroscopy.
Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    
% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
Comparisons against the reaction modeling codes  CoH, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
% \textred{
Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded from proton fluence determination.
% }
% \textred{
To avoid inadvertently reporting enhanced proton fluence, the use of silicone adhesives for aluminum monitor foils is strongly discouraged.
% }

@@

\begin{figure}
 \centering
 \includegraphics[scale=0.1,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
 % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
 \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place. The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell. The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.  }
\end{figure}

@@

The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
\comment{Insert text here to describe our Na22 / Si production hypothesis.  }
It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
This phenomenon is observed for the \ce{^{nat}Cu}(p,x)\ce{^{56}Co} monitor reaction as well, though to a much smaller degree.
In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils. 
The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively. 
The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
This serves as an example of the importance of selecting monitor reaction products inaccessible through (n,x) channels, as noted previously.
However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.

\begin{figure}
 \centering
 \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
 \caption{Result of the variance minimization performed by adjusting the degrader density in MCNP6 simulations of the target stack.  A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.52\% greater than nominal. The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
 \comment{Stephen: Half-width figure: Larger text and axes tick-marks would be nice. }
 \label{fig:variation_curve}
\end{figure}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[scale=0.59]{a)}{./figures/before_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:before_minimization}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[scale=0.59]{b)}{./figures/after_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:after_minimization}
    \end{subfigure}%
    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%. A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
     \label{fig:variance_mins}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:before_subtraction}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[scale=0.59]{b)}{./figures/after_subtraction_plot.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:after_subtraction}
    \end{subfigure}%
    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by activation through (n,x) reactions from the secondary neutron flux. By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
     \label{fig:na_subtraction}
\end{figure*}

Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the 6 irradiated Nb foils in \autoref{fig:Nb_ptallies}. 
As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail-ratio increases as more  secondary protons are produced upstream.
As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.

@@

\begin{figure}
 \centering
 \includegraphics[scale=.8]{./figures/fluence_plot.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Final weighted-fit proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions. A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. A clear loss of fluence  is visible, dropping by approximately 8.1\% from the incident fluence of 202.2 nAh over the length of the target stack.  This is due to a combination of beam utilization, as well as scattering.}
 \comment{Stephen:  Half-width figure: Larger text and axes tick-marks would be nice. }
 \label{fig:fluence_plot}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=.8]{./figures/Nb_ptallies.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6. The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations. As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
 \comment{Stephen: Half-width figure: Larger text and axes tick-marks would be nice. }
 \label{fig:Nb_ptallies}
\end{figure}

@@

After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
\comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   shows the location where the primary proton beam was incident upon the foil.
Based on the \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the average fluence at each energy position (seen in \autoref{fig:fluence_plot}), a fluence of 202.2$\pm$5.4 nAh was calculated to be incident upon the target stack, which shows excellent agreement with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
This incident fluence dropped by approximately 8.1\% to  185.9 $\pm$3.4 nAh over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

@@

>>>>

Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions needed to establish beam characteristics in this energy range needed to perform quantitative cross section measurements.  
To address this need, a target stack consisting of thin Nb, Cu, and Al monitor foils using a 100 MeV proton beam at the Los Alamos National Laboratory's Isotope Production Facility was irradiated in order to establish \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} as a reaction monitor for intermediate energy protons and to benchmark state-of-the-art reaction model codes in this energy region.
% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
Cross sections were measured using the well-characterized 
% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence determination, with all activities quantified using high-purity germanium spectroscopy.
Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    
% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
Comparisons against the reaction modeling codes  CoH, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
% \textred{
Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
% }
% \textred{
To avoid inadvertently reporting enhanced proton fluence, the use of silicone adhesives for aluminum monitor foils is strongly discouraged.
% }

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
 % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
 \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place. The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell. The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.  }
\end{figure}

@@

\begin{figure}
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.5\linewidth]{./figures/variation_curve-crop.pdf}

 % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
 \caption{Result of the variance minimization performed by adjusting the degrader density in MCNP6 simulations of the target stack.  A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.52\% greater than nominal. The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
 \label{fig:variation_curve}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[scale=0.59]{a)}{./figures/before_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:before_minimization}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[scale=0.59]{b)}{./figures/after_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:after_minimization}
    \end{subfigure}%
    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%. A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions. Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
     \label{fig:variance_mins}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[scale=0.57]{a)}{./figures/Na22_activity_compare.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:Na22_activity_compare}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[scale=0.57]{b)}{./figures/Na24_activity_compare.pdf}{180}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:Na24_activity_compare}
    \end{subfigure}%
    \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections. At low energies, experimentally observed apparent \ce{^{22,24}Na} activities in each Al foil packet are consistent with IAEA recommendations, but diverge at higher energies as the \ce{^{nat}Si}(p,x)\ce{^{22}Na} exit channels begin to open up. \ce{^{22,24}Na} activities consistent with TENDL-2015 estimates are observed in each Nb and Cu foil packet as well, confirming that contamination may be attributed to activation of silicone adhesives.}
     \label{fig:Na_activity_compare}
\end{figure}

The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
% \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0 MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6 MeV), though to a much smaller degree.
In both cases, this disparity is caused by the fact that the Kapton tape used for sealing foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\% \ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3 MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6 MeV).
\ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.

These compensating factors  contribute to \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} production being competitive with the \ce{^{nat}Al}(p,x)\ce{^{22}Na} production route.
This is made made obvious when comparing the total measured activities of \ce{^{22}Na} and \ce{^{24}Na} in each Al foil packet (which combines both Al- and Si-based production routes), relative to the expected EoB activities for each reaction channel, presented in \autoref{fig:Na_activity_compare}.
Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
Several observations are immediately obvious.
At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.  
At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90 MeV.
For the \ce{^{24}Na} production, we see a similar behavior, though since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude, only a minor increase in apparent \ce{^{24}Na} activity is seen.
The measured EoB \ce{^{22}Na} and \ce{^{24}Na} activities seen  in all Cu and Nb foil positions are also shown here, which are seen to be consistent with the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{22}Na} yields. 
The observed \ce{^{24}Na} activities also follow the shape of the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{24}Na} yields, albeit smaller in magnitude at the higher energy positions.

While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to the number of assumptions involved in such a calculation.
The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
These have been taken as 10\% (stoichiometric basis) and 4.79 mg/cm$^2$ (based on bulk density), respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
In principle, it would be possible  to subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
The results of this  may be seen in \autoref{fig:na_subtraction} --- following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
% In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
% Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils. 
% The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively. 
% The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
This serves as a pointed example of the importance of selecting monitor reaction products inaccessible through channels aside from the primary reaction (\ce{^{nat}Al}(p,x)\ce{^{22,24}Na}, in this case ), as noted previously.
% However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.

% Avoud using al and silicone

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:before_subtraction}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[scale=0.59]{b)}{./figures/after_subtraction_plot.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:after_subtraction}
    \end{subfigure}%
    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets. Following subtraction of \ce{^{22,24}Na} activities observed in the silicone adhesive of Nb and Cu foils in the same energy \enquote{compartment}, the consistency of the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction improves  dramatically.  By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
     \label{fig:na_subtraction}
\end{figure}

Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the 6 irradiated Nb foils in \autoref{fig:Nb_ptallies}. 
As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail ratio increases as more  secondary protons are produced upstream.
As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth]{./figures/Nb_ptallies.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6. The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations. As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
 \label{fig:Nb_ptallies}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Final weighted-fit proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions. A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. A clear loss of fluence  is visible, dropping by approximately 8.1\% from the incident fluence of 202.2 nAh over the length of the target stack.  This is due to a combination of beam utilization, as well as scattering.}
 \label{fig:fluence_plot}
\end{figure}

@@

After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   shows the location where the primary proton beam was incident upon the foil.
Based on the \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the average fluence at each energy position (seen in \autoref{fig:fluence_plot}), a fluence of 202.2$\pm$5.4 nAh was calculated to be incident upon the target stack, which shows excellent agreement with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
This incident fluence dropped by approximately 8.1\% to  185.9 $\pm$3.4 nAh over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

@@

First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.  We intend to do the same for our next proton irradiation at LBL.

We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.  This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
